Bricking up backdoors in Intrusion Detection Systems

### 2019-09-16 paper/paper.tex
Modified references

\paragraph{\gls{ml} Techniques}
%\subsubsection{Deep Learning}
We used PyTorch~\cite{paszke2017automatic} to build an \gls{mlp}. 
% neural network classifier.
For this we used 5 fully connected layers with 512 neurons each. We applied \gls{relu} activation after each layer and dropout with a probability of 0.2 and used binary cross entropy  as loss function for training. % for the classification task itself.

%\subsubsection{\glspl{rf}}
In addition to the \gls{mlp}, we trained an \gls{rf} classifier to detect attacks in network traffic. We used the RandomForestClassifier implementation from scikit-learn~\cite{pedregosa_scikit-learn:_2011} for this task and used 100 estimators for training the \gls{rf}.

>>>>

\paragraph{\gls{ml} Techniques}
%\subsubsection{Deep Learning}
We used PyTorch~\cite{paszke_automatic_nodate} to build an \gls{mlp}. 
% neural network classifier.
For this we used 5 fully connected layers with 512 neurons each. We applied \gls{relu} activation after each layer and dropout with a probability of 0.2 and used binary cross entropy  as loss function for training. % for the classification task itself.

%\subsubsection{\glspl{rf}}
In addition to the \gls{mlp}, we trained an \gls{rf} classifier to detect attacks in network traffic. We used the RandomForestClassifier implementation from scikit-learn~\cite{pedregosa_scikit-learn_2011} for this task and used 100 estimators for training the \gls{rf}.
